\section*{Industry Fundamentals}

Overall IT spending has been growing at an annual rate of about 2-3\%, while cloud-based software, big data analytics, and cybersecurity are expected to remain growth areas.\autocite[]{CloudAnalyticsCybersecurityApplication}\autocite[]{CIOIntro}
The public cloud market is expected to increase from \$58bn in 2013 to \$101bn by 2020, with the market for cloud applications growing to \$133bn over the same period.\autocite[]{CIOIntro}
Cloud systems tend to be more scalable and easy to use than in house solutions.\autocite[]{CIOIntro}

Cloud computing is really just a model of renting storage and processing time to clients.\autocite[]{AftermathOfIntegratedStack}
The real advantage of cloud computing is that the host can take advantage of far greater economies of scale than their individual clients could on their own, pushing down costs dramatically.\autocite[]{AftermathOfIntegratedStack}
Integrated stacks can lower the cost of deploying new enterprise software solutions, whereas in the past most of the expense involved in deploying new software was actually in having internal IT departments integrate all of the diverse tools and platforms integrated stacks can be purchased deployed and maintained quickly and cheaply.\autocite[]{AftermathOfIntegratedStack}
Cloud service providers also integrate their own tools into their offerings to help their costumers use and manage their cloud resources.\autocite[]{AftermathOfIntegratedStack}
There is a growing shift towards more ``transparent'' IT solutions which try to hide from the end user with more embedded and cloud based applications.\autocite[]{OptimismInnovation}

Some analysts believe that google is ``very much behind in this game'' with regards to cloud computing.\autocite[]{GoogleCloudBoost}
Amazon in particular is considered to be very strong in the cloud business.  Industry analysts describes Amazon Web Services as being ``so robust with rich services, most of which are products of iterative enhacement that I think it will be very difficult for any company, including Google to catch up.''\autocite[]{GoogleCloudBoost}
Amazon's cloud business grew 78\% year over year recently.\autocite[]{GoogleCloudBoost}

Microsoft's emphasis on their Azure cloud platform represents a major shift for the company as it tries to push its way into a into an already competitive and crowded field.\autocite[]{OptimismInnovation}
Microsoft is currently encouraging users to shift from Office  to Office 365, their cloud based alternative.\autocite[]{NextGenBusinessSoftware}
Vmware is another signficant player in the data-center business. Their focus being upon virtualization technologies that are becoming an increasing common in these sorts of environments.\autocite[]{NextGenBusinessSoftware}
Virtualization is another important technology that has begun to play a significant role over the past few tears.\autocite[]{LargeParadigmShiftCloudComputing}
Virtualization allows multiple operating systems and software stacks to be hosted upon a server by introducing a layer of abstraction between the operating systems and the raw hardware of the host machine.\autocite[]{LargeParadigmShiftCloudComputing}

Software as a service is growing component of the software industry and holds several key advantages over more traditional sales models, most importantly in terms of cost and ease of deployment.\autocite[]{GrowthTrendsSoftwareService}\autocite[]{TransitionPhaseEnterpriseApplication}
The computer service and support industry is heavily dependent upon the relationship of trust between the service provider and the consumer, who usually have to base their decision of of references.\autocite[9]{buxmann2012software}
The rise of cloud computing has made it far easier for the consumers of enterprise software products to try out different products and shop between competing vendors before making a potentially risky deal.\autocite[29]{LiquidLunch}
As a result vendors are forced to compete more upon substance.\autocite[29]{LiquidLunch}. This change has been reflected amongst the ranks of salesmen who have seen a dramatic growth in wage disparity between the most and least successful representatives as those with technical knowledge of their products have come into much higher demmand.\autocite[30]{LiquidLunch}

Oracle has decided not follow Amazon in offering raw computing and data storage services. Oracle co-CEO Mark Hurd claimed that the decision was based upon the low margins of raw services like Amazon's.\autocite[]{OracleCloudNotAWS}
Oracle has a tremendous sales force with roughly 30,000 employees all over the globe in order to attract customers.\autocite[]{OracleCloudNotAWS}
Amazon has not yet invested in trying to develop enterprise applications hosted on its own cloud infrastructure. However both SAP and Oracle have begun to ramp up their cloud based services with choosing to build on top of the AWS platform.\autocite[]{OracleCloudNotAWS}
Oracle largely missed the bus in the cloud hosting business given that it would likely cost billions of dollars to acquire the talent, resources, and know-how in order to compete with the current industry leaders.\autocite[]{OracleCloudNotAWS}
Oracle co-CEO Mark Hurd reported that ``We now have virtually 100\% of our portfolio rewritten, rebuilt and modernized for the cloud.''\autocite[]{OracleRebuilt}
Cloud based services have seen exceptionally rapid adoption, Oracle added 200 new ERP customers over the last quarter, and has drawn approximately \$5 billion dollars in research and development investment.\autocite[]{OracleRebuilt}
Oracle's cloud base business offerings still only account for 7\% of total revenue.\autocite[]{OracleNoGrowth}
Oracle has seen its other business stagnate and decline in the meanwhile.\autocite[]{OracleNoGrowth}
Microsoft and Red Hat have reached an agreement to bring Red Hat's enterprise Linux operating system to the Microsoft Azure cloud.\autocite[]{MSRHTDeal}
Microsoft plans to market Red Hat Linux as the ``preferred'' option for enterprise-level customers using the Azure platform with both companies collaborating to provide support.\autocite[]{MSRHTDeal}

There has been a major shift towards using software to help analyze data in order to make decisions and draw insights that would otherwise be beyond the reach of a human observer.\autocite[]{NextGenBusinessSoftware}
The capacity to extract useful information from huge piles of data, such as tweets or facebook posts.\autocite[]{NextGenBusinessSoftware}
Naturaly privacy is a big concern, but many modern technology platforms operate upon the assumption that the user doesn't care about privacy at all. Services like free email, cloud storage, and social networking almost invariably require the end user to give up any real expectation of privacy. Moreover many of these business are directly dependent upon gathering their users data in order to turn a profit.\autocite[]{NextGenBusinessSoftware}
